%==========================================================================
\section{Related Work}
\label{sec:related}

\textbf{Vision-and-Language Navigation.}
R2R~\cite{anderson2018r2r} set the indoor instruction-following task on the
Matterport3D graph~\cite{chang2017matterport}; later benchmarks widened it to
multilingual instructions, continuous control, and object-oriented
goals~\cite{ku2020rxr,krantz2020vlnce,zhu2021soon}, and the agents evolved
from sequence models~\cite{fried2018speakerfollower,tan2019envdrop} to the
transformer policies we test~\cite{chen2022duet,chen2021hamt,hong2021vlnbert},
surveyed in~\cite{zhang2024survey}. A parallel thread gives the agent a sense
of its own progress, from progress estimation~\cite{ma2019selfmonitoring} to
asking for help when the instruction leaves out needed
information~\cite{abraham2025ask}, but these internal signals come with no
finite-sample statement about how often the correct move is retained, the gap
a calibrated set is meant to close.

\textbf{Uncertainty without a distribution-free guarantee.}
Deep classifiers are miscalibrated and
overconfident~\cite{guo2017calibration}; Bayesian and ensemble methods
approximate a posterior~\cite{gal2016dropout,lakshminarayanan2017ensembles},
and classical robotics propagates an explicit probabilistic
state~\cite{thrun2005probabilistic}. None certifies coverage at a chosen risk
level in finite samples, the property a help-seeking robot needs before it
defers to a person.

\textbf{Conformal prediction and its scores.}
CP turns any score into a set with a finite-sample, distribution-free
coverage guarantee under
exchangeability~\cite{vovk2005alrw,lei2018distributionfree,angelopoulos2023gentle}.
The standard classification scores, THR~\cite{sadinle2019least},
APS~\cite{romano2020aps}, and RAPS~\cite{angelopoulos2021raps}, were built
for i.i.d.\ prediction, and scaling a score by an estimate of its local
difficulty is an old idea in regression
CP~\cite{papadopoulos2011normalized}. None was designed for a policy whose
scores concentrate near zero (Section~\ref{ssec:failure}); our normalisation
is a parameter-free instance of that scaling aimed at the concentration.

\textbf{CP for robot decisions.}
KnowNo defers to a human when the set grows past a
singleton~\cite{ren2023knowno}, introspective planning aligns an LLM
planner's set with task ambiguity~\cite{liang2024introspective}, and CP has
entered model predictive control~\cite{lindemann2023conformal} and
multi-agent motion planning~\cite{dixit2023multiagent}. These wrap a standard
score, taken as given, around a single decision or a low-dimensional
trajectory; that score is exactly what fails on the concentrated policies of
sequential navigation, and it is what we redesign.

\textbf{Dependence, graphs, and covariate shift.}
CP beyond exchangeability prices the loss when units
depend~\cite{barber2023beyond}, and node-level graph CP conformalises over
graph nodes~\cite{huang2023graphcp,zargarbashi2023graphcp}; our reduction
instead makes the walk the exchangeable unit. Under shift, adaptive CP tracks
the threshold online~\cite{gibbs2021aci} and weighted CP corrects coverage
when a likelihood ratio is estimable~\cite{tibshirani2019covariateshift},
both of which we evaluate in Section~\ref{sec:disc}. The compounding of an
early error along a sequential policy also motivates no-regret imitation
learning~\cite{ross2011reduction}; our episode-level unit absorbs it
outright, since Theorem~\ref{thm:cov} never asks the steps of one walk to be
independent.
