%==========================================================================
\section{Method: Zero-Shot Normalised CP}
\label{sec:method}
The method has three deterministic phases, a confidence-adjusted score, an
episode-level calibration unit, and a deployed threshold. It holds no
trainable parameters and adds no latency.

\subsection{The confidence-adjusted nonconformity score}
\label{ssec:score}
To counter the concentration of Section~\ref{ssec:failure} we rescale any
base score $\sbase \in \{s_{\mathrm{THR}}, s_{\mathrm{APS}},
s_{\mathrm{RAPS}}\} of \eqref{eq:thr}--\eqref{eq:raps}$ by a parameter-free proxy read straight off the policy
confidence $\pmax = \max_a \pi_\theta(a\mid L, x_t, h_t)$,
\begin{equation}
\snorm(x_t, a) \;=\; \frac{\sbase(x_t, a)}{1 + \big(1 - \pmax\big)}
\;=\; \frac{\sbase(x_t, a)}{2 - \pmax}.
\label{eq:snorm}
\end{equation}
The denominator $1 + (1-\pmax)$ is one positive scalar shared by every
candidate at step $t$, so \eqref{eq:snorm} rescales the scores and keeps their
order. On a confident step $\pmax \approx 1$, the denominator goes to $1$ and
$\snorm \approx \sbase$, so easy steps are left alone and the set does not
grow. On an uncertain step $\pmax$ is low, the denominator grows, $\snorm$
shrinks, more candidates pass the threshold, and the set widens where the
robot is confused. The membership test $\snorm(x,a) \leq \hat q$ rewrites
to $\sbase(x,a) \leq \hat q\,(2 - \pmax)$, a base score read against a
confidence-adaptive threshold, and evaluating it costs one subtraction per
step. The set ranges over the valid candidates of $\mathcal{A}_t$, so a masked
action with $p_a = 0$ is never included, and $|\mathcal{A}_t|$ in what follows
is the number of valid candidates.

\subsection{Episode-maximum calibration unit}
\label{ssec:epmax}
Per-step pairs within an episode share $h_t$ and are not exchangeable, so
step-pooled calibration breaks the CP requirement and gives no guarantee on
whole-trajectory survival. We reduce each calibration episode $e$ (steps
$1\dots T_e$, teacher actions $a^*_t$) to a single most-surprising correct
score,
\begin{equation}
\tilde{s}_e \;=\; \max_{t \in \{1,\dots,T_e\}} \snorm(x_{e,t}, a^*_{e,t}),
\label{eq:epmax}
\end{equation}
which restores exchangeability at the episode level and targets simultaneous
coverage over the walk (Theorem~\ref{thm:cov}).

\subsection{Threshold and test-time inference}
\label{ssec:infer}
Given $\alpha$ and $n$ exchangeable calibration episodes, the threshold is
the corrected quantile of the episode-maximum scores,
\begin{equation}
\hat q(\alpha) = \mathrm{Quantile}\Big(\{\tilde s_1,\dots,\tilde s_n\};\,
\tfrac{\lceil(n+1)(1-\alpha)\rceil}{n}\Big).
\label{eq:qhat-ep}
\end{equation}
Because the score is fixed and parameter-free, all $n$ calibration episodes
are exchangeable with the test episode, so there is no train-calibrate split
and $n$ is the full calibration set (Remark~\ref{rem:paramfree}). At test time
the agent extracts $\pmax$ from its softmax and forms
\begin{equation}
C_\alpha(x_t) = \{a \in \mathcal{A}_t : \snorm(x_t, a) \leq \hat q(\alpha)\},
\label{eq:set}
\end{equation}
with the $\arg\max$ action as fallback when the set is empty. There is no
training loop, and Section~\ref{sec:disc} closes the loop by querying an
operator when the set grows.


Section~\ref{sec:guarantee}, next, states and proves the exact finite-sample
guarantee this pipeline satisfies, at every level $\alpha$, with the full
calibration set behind the quantile because the score holds nothing to fit.
