%==========================================================================
\section{The Coverage Guarantee}
\label{sec:guarantee}
Everything the pipeline promises rests on one theorem, stated and proved in
full. The quantile step is the classical split-conformal
argument~\cite{vovk2005alrw,lei2018distributionfree,angelopoulos2023gentle},
taken in the tie-robust counting form of
\cite[Lemma~1]{tibshirani2019covariateshift}; what is new is the object it
is applied to, the episode maximum of a parameter-free score, which makes
the walk the exchangeable unit.

\textit{Setting.}
An episode record $E$ collects everything one rollout of the fixed policy
produces: the instruction $L$, the visited states $x_1,\dots,x_T$ with their
admissible sets $\mathcal A_t$ and softmax $\{p_a\}_{a\in\mathcal A_t}$, the
teacher actions $a^*_t\in\mathcal A_t$, and the length $T=T(E)$. The reduced score $\tilde s=\varphi(E)$ of \eqref{eq:epmax} is one fixed
measurable function of the record, chosen before any calibration data are
seen; that is the exact content of parameter-freeness.

\begin{assumption}[Exchangeable episodes]
\label{asm:exch}
The joint law of the episode records $(E_1,\dots,E_n,E_{n+1})$, calibration
plus test, is invariant under permutations of the $n+1$ indices. Episodes
drawn i.i.d.\ from one task distribution are a special case.
\end{assumption}

Assumption~\ref{asm:exch} leaves steps inside an episode arbitrarily
dependent, the policy arbitrarily miscalibrated, lengths variable, and the
scores free to carry atoms such as the point mass at zero of
Section~\ref{ssec:failure}.

\begin{theorem}[Simultaneous coverage at every level]
\label{thm:cov}
Fix any $\alpha\in(0,1)$, let $k=\lceil(n+1)(1-\alpha)\rceil$, and let
$\hat q(\alpha)$ be the $k$-th smallest of $\tilde s_1,\dots,\tilde s_n$ as in
\eqref{eq:qhat-ep}, with $\hat q(\alpha)=+\infty$ when $k>n$. Under
Assumption~\ref{asm:exch}, the test episode $E_{n+1}$, with steps
$t=1,\dots,T_{n+1}$, satisfies
\begin{equation}
\mathbb{P}\big(a^*_t\in C_\alpha(x_t)\ \text{for all } t\big)\;\geq\;1-\alpha .
\label{eq:thm-cov}
\end{equation}
\end{theorem}

\begin{proof}
Write $Z_i=\varphi(E_i)=\tilde s_i$ for $i=1,\dots,n+1$ and abbreviate
$\hat q=\hat q(\alpha)$.

\emph{Step 1 (the trajectory event is one scalar comparison).}
By the membership rule \eqref{eq:set}, $a^*_t\in C_\alpha(x_t)$ if and only if
$\snorm(x_t,a^*_t)\leq\hat q$, and the teacher action is always an admissible
candidate, $a^*_t\in\mathcal A_t$. Taking the conjunction over the steps of
the test episode,
\begin{equation}
\begin{split}
\{a^*_t\in C_\alpha(x_t)\ \forall t\}
&=\Big\{\max_{t\leq T_{n+1}}\snorm(x_t,a^*_t)\leq\hat q\Big\}\\
&=\{Z_{n+1}\leq\hat q\}.
\end{split}
\label{eq:event}
\end{equation}
The empty-set fallback of Section~\ref{ssec:infer} only ever adds an action to
the deployed set, so \eqref{eq:thm-cov} holds a fortiori for the deployed
sets once it holds for \eqref{eq:set}.

\emph{Step 2 (exchangeability survives the reduction).}
The map $\varphi$ is measurable and fixed before any data are seen, so for
every permutation $\pi$ of $\{1,\dots,n+1\}$,
\begin{align*}
(Z_{\pi(1)},\dots,Z_{\pi(n+1)})
&=\big(\varphi(E_{\pi(1)}),\dots,\varphi(E_{\pi(n+1)})\big)\\
&\overset{d}{=}(Z_1,\dots,Z_{n+1})
\end{align*}
by Assumption~\ref{asm:exch}. Hence $Z_1,\dots,Z_{n+1}$ are exchangeable:
exchangeability is closed under a fixed measurable map applied
coordinatewise (see, e.g.,~\cite{kallenberg2005symmetries}). This is the
step a fitted score breaks (Remark~\ref{rem:paramfree}).

\emph{Step 3 (the quantile bound, ties allowed).}
If $k>n$, which happens only when $\alpha<\tfrac{1}{n+1}$, then
$\hat q=+\infty$, every candidate passes the test, and \eqref{eq:thm-cov} is
trivial, so let $k\leq n$. Let $q^\star$ be the $k$-th smallest of all $n+1$
values $Z_1,\dots,Z_{n+1}$. Two facts finish the proof.

(i) \emph{Deterministically, $Z_{n+1}\leq q^\star$ implies
$Z_{n+1}\leq\hat q$.} Sort the $n+1$ values as
$v_{(1)}\leq\dots\leq v_{(n+1)}$, so $q^\star=v_{(k)}$. If
$Z_{n+1}\leq v_{(k)}$, some position $p\leq k$ carries the value $Z_{n+1}$,
for otherwise every copy of $Z_{n+1}$ would sit above position $k$ and
force $v_{(k)}<Z_{n+1}$. Removing the entry at position $p$ leaves, as a
multiset, exactly the $n$ calibration scores, whose $k$-th smallest is
$v_{(k+1)}\geq v_{(k)}\geq Z_{n+1}$; that $k$-th smallest is $\hat q$.

(ii) \emph{By exchangeability, $\mathbb{P}(Z_{n+1}\leq q^\star)\geq
k/(n+1)$.} The threshold $q^\star$ is a symmetric function of
$(Z_1,\dots,Z_{n+1})$, so by Step~2 the pairs $(Z_i,q^\star)$ share one joint
law and the probabilities $\mathbb{P}(Z_i\leq q^\star)$ are equal across
$i$. By the definition of the $k$-th order statistic, counting multiplicity,
$\#\{i:Z_i\leq q^\star\}\geq k$ holds surely. Taking expectations,
\[
k\;\leq\;\sum_{i=1}^{n+1}\mathbb{P}(Z_i\leq q^\star)
\;=\;(n+1)\,\mathbb{P}(Z_{n+1}\leq q^\star).
\]
Combining (i), (ii), and \eqref{eq:event},
\begin{align*}
\mathbb{P}\big(a^*_t\in C_\alpha(x_t)\ \forall t\big)
&=\mathbb{P}(Z_{n+1}\leq\hat q)\\
&\geq\frac{k}{n+1}
=\frac{\lceil(n+1)(1-\alpha)\rceil}{n+1}
\geq 1-\alpha .
\end{align*}

\end{proof}

The guarantee is marginal, over the joint draw of calibration and test
episodes, which is the standard form of split-conformal
validity~\cite{lei2018distributionfree}; no statement is made conditionally
on one realised calibration set. Nothing in the proof touches the law of
the scores either, so \eqref{eq:thm-cov} holds separately at every
$\alpha\in(0,1)$, atoms push coverage above target, never below, and when
the $\tilde s_i$ are almost surely distinct the same rank count returns the
matching upper bound
$1-\alpha+\tfrac{1}{n+1}$~\cite{vovk2005alrw,lei2018distributionfree,tibshirani2019covariateshift}.
Since $k$ is nonincreasing in $\alpha$ the sets nest, so raising the
tolerated risk can only shrink the set the robot acts on. No union bound is
paid: per-step Bonferroni calibration at level $\alpha/T_{\max}$, the
standard device for multi-horizon conformal
forecasting~\cite{stankeviciute2021cfrnn}, is valid under the same premise
but conservative and tied to a horizon cap fixed in advance, while the
maximum reduction prices the whole variable-length walk at one level
$\alpha$.

\begin{remark}[What the premise excludes]
\label{rem:premise}
Assumption~\ref{asm:exch} is the one door through which deployment can
break \eqref{eq:thm-cov}: a change of law between calibration and
test. Seen-building and unseen-building walks are not
exchangeable, and Section~\ref{ssec:gap} measures what that costs rather than
assuming it away. Recalibrating on episodes from the deployment distribution
restores the premise and the guarantee with it. The premise likewise fixes
the rollout law, so a deployment in which an operator overrides flagged
steps changes that law and calls for recalibration under the assisted
policy.
\end{remark}

\begin{remark}[Why parameter-freeness pays]
\label{rem:paramfree}
Step~2 is where a learned score must spend data, since fitting on a split
disjoint from the quantile's episodes preserves the theorem at the price of
roughly half the calibration set and a second forward pass. The
parameter-free instance skips the split, so all $n=1021$ episodes stand
behind \eqref{eq:qhat-ep}, and the theorem applies to any fixed per-step
scale (Section~\ref{ssec:learned}).
\end{remark}
