%==========================================================================
\section{Experiments}
\label{sec:exp}
We evaluate on R2R~\cite{anderson2018r2r}, calibrating on val-seen
($1021$ episodes) and testing on val-unseen ($2349$ episodes over
disjoint scans). Five backbones span a $16.4$-point success-rate
(SR~\cite{anderson2018spl}, the fraction of episodes that stop within $3$m of
the goal) range and three architecture families, the global
and local action-space settings of DUET~\cite{chen2022duet} (DUET-full and
DUET-local), HAMT~\cite{chen2021hamt}, and Recurrent VLN-BERT under its OSCAR
and PREVALENT initialisations~\cite{hong2021vlnbert}. Each reproduces its
published val-unseen SR to within one point ($71.2$ against $72$, $66.2$
against $66$, $62.8$ against $63$, $58.7$ against $59$). Prediction sets are
recorded and never override the policy, so every run reproduces its baseline
SR exactly. All results use the parameter-free score~\eqref{eq:snorm}.

\subsection{Restored $\alpha$-sensitivity and coverage}
\label{ssec:main}
Table~\ref{tab:main} reports the full grid. The threshold $\hat q$ moves
smoothly with $\alpha$ and never collapses, so the pathology of
Table~\ref{tab:basecp} is gone on all five backbones, and the step-averaged
coverage clears $1-\alpha$ in every one of the $45$ cells; a scan-cluster
bootstrap (episodes cluster by building, so per-episode intervals would be
too narrow) puts the lowest $95\%$ lower confidence bound at $0.943$ (HAMT),
still clear of $0.90$. The same holds on a denser sweep of nine levels
$\alpha\in\{0.05,\dots,0.45\}$: coverage clears its target in all $135$
cells, while base APS and RAPS sit at $\hat q=0$ from $\alpha=0.30$ onward.
The sets are small
in absolute terms, with a mean of $4$ to $7$ at $\alpha = 0.10$, and they
track the action-space degree, largest on DUET-full ($6.8$, whose global
branch decides over the reachable frontier) and near $4$ to $5$ on the
small-action backbones. RAPS keeps zero singletons at $\alpha = 0.10$ and
gives sizes close to THR (for example $5.5$ against $6.8$ on DUET-full); on
the small action spaces there is little tail for its rank penalty to cut.

\input{tables/tab_main}
In the table, cov is step-averaged empirical coverage, $\overline{|C|}$
counts valid candidates (Section~\ref{ssec:score}), and sgl is the singleton
rate; every cov cell clears its target of $1-\alpha$.

\subsection{Coverage gap under shift, and threshold transfer}
\label{ssec:gap}
The simultaneous coverage of Theorem~\ref{thm:cov} (also called
whole-trajectory coverage, the probability that every step of an episode is
covered) falls below $1-\alpha$ under the seen-to-unseen shift. At
$\alpha = 0.10$ it ranges from $0.82$ to $0.89$ across backbones, against the
step-averaged $0.95$ to $0.98$. This is the premise of
Theorem~\ref{thm:cov} at work in reverse. Calibration episodes come from seen
buildings and test episodes from unseen ones, so Assumption~\ref{asm:exch}
fails across that boundary (Remark~\ref{rem:premise}), and the measured
total-variation distance $\dtv = 0.156$ between the two score laws
(Section~\ref{sec:disc}) records how far it fails.

The THR threshold transfers, and we test it directly rather than reading it
off numeric closeness. Applying the threshold calibrated on each backbone to
every other backbone's test split ($20$ cross pairs, THR, $\alpha=0.10$)
holds step coverage between $0.887$ and $1.000$, within $0.013$ of target in
the worst pair, because dividing by $2-\pmax$ maps each backbone onto a
common confidence scale (per-backbone thresholds span $0.981$ to $1.000$).
RAPS varies more because its rank penalty depends on $|\mathcal{A}_t|$. A
transferred threshold is a warm start for a new platform, not a substitute
for recalibration.
